### 2018-08-06 article.tex
2-functor definition and format consistency

\begin{definition}\label{def:PROP}
  A \emph{PROP} is strict symmetric monoidal category whose objects
  are the natural numbers, and where the action of the tensor product on
  objects is given by addition.
\end{definition}

@@

\begin{definition}  \label{def:strict-two-cat}
A \emph{strict} 2-category $\mathcal{C}$ is a category \emph{enriched over
  \textbf{Cat}}, the category of categories, \emph{viz:}
\begin{itemize}
\item A category $\mathcal{C}$, whose objects and arrows are known as
  0-cells and 1-cells respectively.
\item For every pair of objects $A$ and $B$, we have a
  category $\mathcal{C}(A, B)$, whose arrows are known as 2-cells.
\item For 2-cells $\alpha : f \Rightarrow g$ and $\beta : g
  \Rightarrow h$ in $\mathcal{C}(A,B)$ their (vertical) composite is denoted
  $\beta\bullet\alpha : f \Rightarrow h$.
\item For every 1-cell $f:A\to B$ we denote its identity 2-cell by
  $Id_f:f \Rightarrow f$.
\item For all 0-cells $a$, $b$, $c$ a bifunctor $\circ: \mathcal{C}(b, c)
  \times \mathcal{C}(a, b) \to \mathcal{C}(a, c)$ called \emph{horizontal
    composition} of 2-cells.
\end{itemize}
\REM{Need here the name for a 2-cat with all 2-cells invertible;  the
  term 2-groupoid refers to the case where both 1- and 2-cells are
  invertible.}
\end{definition}

@@

\begin{definition}
  \label{def:two-functor}
  DEFINITION OF 2-FUNCTOR here
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{definition}\label{def:monoidal-two-cat}
A \emph{strict} monoidal 2-category $(\mathcal{C}, \otimes)$ is a strict
2-category with
\REM{Is this \emph{required}?  Doesn't it follow from the  definition
  of bifunctor?  (It does in the 1-category case, so it should do
  here!)}
\begin{itemize}
\item a 2-bifunctor $\otimes: \mathcal{C} \times \mathcal{C} \to \mathcal{C}$
  such that on 2-cells $\alpha, \beta, \gamma, \delta$
\[
(\alpha \otimes \beta) \circ (\gamma \otimes \delta) = (\alpha \circ \gamma)
  \otimes (\beta \circ \delta)
\]
\REM{This definition doesn't quite work without the additoin type
  information on the 2-cells}
\end{itemize}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
Since $\circ$ and $\otimes$ are bifunctorial, we have the following
interchange equations for all 0-cells $A, B \in \mathcal{C}$ and all 2-cells
  $\alpha, \beta, \gamma, \delta \in \mathcal{C}(A, B)$
\begin{align}
(\alpha \circ \beta) \bullet (\gamma \circ \delta) &= (\alpha \bullet \gamma)
  \circ (\beta \bullet \delta) \\
(\alpha \otimes \beta) \bullet (\gamma \otimes \delta) &= (\alpha \bullet
  \gamma) \otimes (\beta \bullet \delta)
\end{align}
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
Given a free PROP of quantum circuits, we can extend it to a 2-PROP
  $\mathcal{P}$ where
\begin{itemize}
\item gates form the set of 1-cells 
\item the 2-cells are generated by a finite set of \emph{rewriting} rules such
  that
\begin{itemize}
\item 2 rewriting rules with the same types must be equal
\item each rewriting rule must be invertible, that is $\mathcal{C}(A, B)$ is a
  \emph{groupoid} for all 0-cells $A, B$
\end{itemize}
\end{itemize}

2-cells are in general called \emph{rewrite sequence}, but if a rewrite sequence
  has only 1 occurence of a rewrite rule, it is called an \emph{atomic rule}.
\end{definition}

@@

\begin{proof}
We'll prove it by induction of the size of the rewriting sequence using the
  properties of the bifunctors.
With a atomic rule, we already have
\[
\alpha = \alpha_1
\]
For the inductive step let's assume $\beta$ is
\[
\alpha = \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet \beta
\]
If $s$ is such that
\[
\beta = (\beta_1 \bullet \beta_2) \circ (\beta_3 \bullet \beta_4)
\]
Then using the interchange law we can write
\[
\beta = (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4)
\]
So we have 
\begin{align}
\alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4) \cr
\alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
  \alpha_{i - 1} \bullet \alpha_i
\end{align}
Otherwise we can always add an identity rewriting rule to get the interchange
  law.
\begin{align}
\beta_1 \circ (\beta_3 \bullet \beta_4) &\Rightarrow (\beta_1 \bullet id) \circ
  (\beta_2 \bullet \beta_3) \cr
(\beta_1 \bullet \beta_2) \circ \beta_3 &\Rightarrow (\beta_1 \bullet \beta_2)
  \circ (id \bullet \beta_3)
\end{align}
The same is true with
\[
\beta = (\beta_1 \bullet \beta_2) \otimes (\beta_3 \bullet \beta_4)
\]
\end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
For all rewriting sequences $\alpha: f \Rightarrow g$, $\alpha$ can be writen
\begin{align}
\alpha &= \alpha_1 \circ \alpha_2 \circ \alpha_3 \circ \cdots \circ \alpha_j \cr
\alpha &= \alpha_1 \otimes \alpha_2 \otimes \alpha_3 \otimes \cdots \otimes
  \alpha_k
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        QUANTALE DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Quantale $\mathbb{Q}$]
A quantale is a \emph{lattice} with a binary operator such that for all
  elements of the lattice $x, y$ and $\{x_i\}_i, \{y_i\}_i$
\begin{align}
x \oplus \bigvee y_i &= \bigvee x \oplus y_i \cr
\left(\bigvee x_i\right) \oplus y &= \bigvee x_i \oplus y
\end{align}

We require that for all $x$, it exist $x^{-1}$ such that
\begin{align}
x \oplus x^{-1} &= e \cr
x^{-1} \oplus x &= e
\end{align}

@@

On gates
\begin{align}
V(f \circ g) &\preceq V(f) \oplus V(g) \cr
V(f \otimes g) &\preceq V(f) \oplus V(g)
\end{align}

On rewriting sequences
\begin{align}
V(\alpha \circ \beta) &= V(\alpha) \oplus V(\beta) \cr
V(\alpha \otimes \beta) &= V(\alpha) \oplus V(\beta) \cr
V(\alpha \bullet \beta) &= V(\alpha) \oplus V(\beta)
\end{align}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
Note that because
\[
V(\alpha: f \Rightarrow g) = V(f) \oplus V(g)^{-1}
\]
then
\begin{align}
V(\alpha: f \Rightarrow f) &= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
that is
\begin{align}
\forall f, V(id_f) = e
\end{align}
\end{remark}

@@

\begin{proof}
The set of all possible rewriting sequences is freely generated by the set of
rewriting rules, $\bullet$, $\circ$ and $\otimes$ so both $\alpha$ and $\beta$
  can be written
\begin{align}
\alpha &= \alpha_1 \odot \alpha_2 \odot \alpha_3 \odot \cdots \odot \alpha_n \cr
\beta &= \beta_1 \odot \beta_2 \odot \beta_3 \odot \cdots \odot \beta_m
\end{align}
with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i $\alpha_i$ and
$\beta_i$ are rewriting rule.
If $n = 1$ then $\alpha$ is a rewriting rule, so $V(r) = V(f) \oplus V(g)^{-1}$.
Otherwise
\begin{align}
V(\alpha) &= V(\alpha_1 \odot \alpha_2 \odot \cdots \odot \alpha_n) \cr
&= V(\alpha_1) \oplus V(\alpha_2) \oplus \cdots \oplus V(\alpha_n) \cr
&= V(f \Rightarrow h_1) \oplus V(h_1 \Rightarrow h_2) \oplus \cdots \oplus
  V(h_n \Rightarrow g) \cr
&= V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus \cdots
  \oplus V(h_n) \oplus V(g)^{-1}
\end{align}
A easy inductive proof can show us that
\[
V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus V(h_2) \oplus
  \cdots \oplus V(h_n) \oplus V(g)^{-1} = V(f) \oplus V(g)^{-1}
\]
The same is true for $\beta$, so
\[
V(\alpha) = V(\beta) = V(f) \oplus V(g)^{-1}
\]
\end{proof}
\end{proposition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
The following category $\mathcal{P}(\mathbb{Q})$ is a $\mathbb{Q}$-category
\begin{itemize}
\item A set of objects which are the gates of $\mathcal{P}$
\item For all objects $(f, g)$
\end{itemize}
\[
\mathcal{E}(f, g) =
\begin{cases}
\textrm{if } f \Rightarrow g \in \mathcal{P}, &V(f \Rightarrow g) \cr
\textrm{otherwise } &\top
\end{cases}
\]
With $\top \in \mathbb{Q}$ such that for all $x \in \mathbb{Q}$
\[
x \preceq \top
\]

\begin{proof}
For all gates $(f, g)$, if it exists a unique transformation $f \Rightarrow
  g$, then
\begin{align}
\mathcal{E}(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \cr
&= V(f) \oplus V(g)^{-1}
\end{align}
otherwise we already have $\mathcal{E}(f, g) = \top \in \mathbb{Q}$.
For all gates $f$, we know that there is a identity transformation $f
  \Rightarrow f$ and
\begin{align}
\mathcal{E}(f, f) &= V(id_f) \cr
&= V(f \Rightarrow f)\cr
&= V(f) \oplus V(f)^{-1} \cr
&= e
\end{align}
Finally, for all gates $(f, g, h)$ such that there exists $\alpha: f \Rightarrow
  g$ and $\beta: g \Rightarrow h$ in $\mathcal{P}$, then the homomorphism $V$
    give us
\begin{align}
\mathcal{E}(f, h) &= V(f \Rightarrow h) \cr
&= V(\alpha \circ \beta) \cr
&= V(\alpha) \oplus V(\beta) \cr
&= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \cr
&= \mathcal{E}(g, h) \oplus \mathcal{E}(f, g)
\end{align}
If either $\alpha$ or $\beta$ doesn't exists in $\mathcal{P}$ then
\[
\mathcal{E}(b, c) \oplus \mathcal{E}(a, b) \succeq \mathcal{E}(a, c)
\]
become
\[\begin{matrix}
&\mathcal{E}(b, c) \oplus \top &\succeq \top \cr
\textrm{or} &\top \oplus \mathcal{E}(a, b) &\succeq \top \cr
\textrm{or} &\top \oplus \top &\succeq \top
\end{matrix}\]
which is still true.
\end{proof}
\end{proposition}

@@

\begin{proof}
The monoidal structure is immediate using the fact that
\[
V(\alpha) \oplus V(\beta) \succeq V(\alpha \otimes \beta)
\]
that is
\[
V(\alpha: f \Rightarrow g) \oplus V(\beta: f' \Rightarrow g') = V(\alpha \otimes
  \beta: f \otimes f' \Rightarrow g \otimes g')
\]
so
\[
\mathcal{E}(f, g) \oplus \mathcal{E}(f', g') = \mathcal{E}(f \otimes f', g
  \otimes g')
\]
For the symmetry, we use the fact that $V(f \Rightarrow g) \oplus V(g
  \Rightarrow f) = e$
\begin{align}
\mathcal{E}(f \otimes g, g \otimes f) &= V(f \otimes g \Rightarrow g \otimes g)
  \cr
&= V(f \Rightarrow g \otimes g \Rightarrow f) \cr
&\preceq V(f \Rightarrow g) \oplus V(g \Rightarrow f) \cr
&= V(f) \oplus V(g)^{-1} \oplus V(g) \oplus V(f)^{-1} \cr
&= e
\end{align}
\end{proof}
\end{proposition}

>>>>

\begin{definition} \label{def:PROP}
  A \emph{PROP} is strict symmetric monoidal category whose objects
  are the natural numbers, and where the action of the tensor product on
  objects is given by addition.
\end{definition}

@@

\begin{definition}  \label{def:strict-two-cat}
  A \emph{strict} 2-category $\mathcal{C}$ is a category \emph{enriched over
    \textbf{Cat}}, the category of categories, \emph{viz:}
  \begin{itemize}
    \item A category $\mathcal{C}$, whose objects and arrows are known as
      \emph{0-cells} and \emph{1-cells} respectively.
    \item For every pair of objects $A$ and $B$, we have a
      category $\mathcal{C}(A, B)$, whose arrows are known as \emph{2-cells}.
    \item For \emph{2-cells} $\alpha : f \Rightarrow g$ and $\beta : g
      \Rightarrow h$ in $\mathcal{C}(A,B)$ their (vertical) composite is denoted
      $\beta \bullet \alpha : f \Rightarrow h$.
    \item For every 1-cell $f:A\to B$ we denote its identity 2-cell by
      $Id_f:f \Rightarrow f$.
    \item For all \emph{0-cells} $a$, $b$, $c$ a bifunctor $\circ:
      \mathcal{C}(b, c) \times \mathcal{C}(a, b) \to \mathcal{C}(a, c)$ called
      \emph{horizontal composition} of \emph{2-cells}.
  \end{itemize}
\REM{Need here the name for a 2-cat with all \emph{2-cells} invertible;  the
  term 2-groupoid refers to the case where both 1- and \emph{2-cells} are
  invertible.}
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        2-FUNCTOR DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition} \label{def:two-functor}
  A \emph{strict} 2-functor $F$ between two \emph{strict} 2-categories
    $\mathcal{C}$ and $\mathcal{D}$ is
  \begin{itemize}
    \item for all \emph{0-cells} $A \in \mathcal{C}$ a 0-cell $F(A) \in
      \mathcal{D}$
    \item for all \emph{0-cells} $(A, B) \in \mathcal{C}$ a functor $F_{A, B}:
      \mathcal{C}(A, B) \to \mathcal{D}(F(A), F(B))$
  \end{itemize}

  \noindent
  Such that $F$ respect the horizontal and vertical compositions.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        MONOIDAL 2-CATEGORY DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}\label{def:monoidal-two-cat}
  A \emph{strict} monoidal 2-category $(\mathcal{C}, \otimes)$ is a strict
    2-category with a 2-bifunctor $\otimes: \mathcal{C} \times \mathcal{C} \to
    \mathcal{C}$.
  \REM{This definition doesn't quite work without the additoin type
    information on the \emph{2-cells}}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        INTERCHANGE LAW REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}[Interchange law]
  Since $\circ$ and $\otimes$ are bifunctorial, we have the following
    interchange equations for all \emph{0-cells} $A, B \in \mathcal{C}$ and all
    \emph{2-cells} $\alpha, \beta, \gamma, \delta \in \mathcal{C}(A, B)$
  \begin{align}
    (\alpha \circ \beta) \bullet (\gamma \circ \delta) &= (\alpha \bullet
      \gamma) \circ (\beta \bullet \delta) \\
    (\alpha \otimes \beta) \bullet (\gamma \otimes \delta) &= (\alpha \bullet
      \gamma) \otimes (\beta \bullet \delta)
  \end{align}
  Since $\otimes$ is a 2-functor, we have for all \emph{0-cells} $A, B \in
    \mathcal{C}$ and all \emph{2-cells} $\alpha, \beta, \gamma, \delta \in
    \mathcal{C}(A, B)$
  \[
    (\alpha \otimes \beta) \bullet (\gamma \otimes \delta) = (\alpha \bullet
      \gamma) \bullet (\beta \bullet \delta)
  \]
\end{remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  Given a free PROP of quantum circuits, we can extend it to a 2-PROP
    $\mathcal{P}$ where
  \begin{itemize}
    \item gates form the set of \emph{1-cells} 
    \item the \emph{2-cells} are generated by a finite set of \emph{rewriting}
      rules such that
    \begin{itemize}
      \item 2 rewriting rules with the same types must be equal
      \item each rewriting rule must be invertible, that is $\mathcal{C}(A, B)$
        is a \emph{groupoid} for all \emph{0-cells} $A, B$
    \end{itemize}
  \end{itemize}

  \emph{2-cells} are in general called \emph{rewrite sequence}, but if a rewrite
    sequence has only 1 occurence of a rewrite rule, it is called an
    \emph{atomic rule}.
\end{definition}

@@

  \begin{proof}
    We'll prove it by induction of the size of the rewriting sequence using the
      properties of the bifunctors.
    With a atomic rule, we already have
    \[
      \alpha = \alpha_1
    \]
    For the inductive step let's assume $\beta$ is
    \[
      \alpha = \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots \bullet
        \beta
    \]
    If $s$ is such that
    \[
      \beta = (\beta_1 \bullet \beta_2) \circ (\beta_3 \bullet \beta_4)
    \]
    Then using the interchange law we can write
    \[
      \beta = (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4)
    \]
    So we have 
    \begin{align}
      \alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots
        \bullet (\beta_1 \circ \beta_3) \bullet (\beta_2 \circ \beta_4) \\
      \alpha &= \alpha_1 \bullet \alpha_2 \bullet \alpha_3 \bullet \cdots
        \bullet \alpha_{i - 1} \bullet \alpha_i
    \end{align}
    Otherwise we can always add an identity rewriting rule to get the
      interchange law.
    \begin{align}
      \beta_1 \circ (\beta_3 \bullet \beta_4) &\Rightarrow (\beta_1 \bullet id)
        \circ (\beta_2 \bullet \beta_3) \\
      (\beta_1 \bullet \beta_2) \circ \beta_3 &\Rightarrow (\beta_1 \bullet
        \beta_2) \circ (id \bullet \beta_3)
    \end{align}
    The same is true with
    \[
      \beta = (\beta_1 \bullet \beta_2) \otimes (\beta_3 \bullet \beta_4)
    \]
  \end{proof}
\end{proposition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        REWRITING SYSTEM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
  For all rewriting sequences $\alpha: f \Rightarrow g$, $\alpha$ can be writen
  \begin{align}
    \alpha &= \alpha_1 \circ \alpha_2 \circ \alpha_3 \circ \cdots \circ \alpha_j
      \\
    \alpha &= \alpha_1 \otimes \alpha_2 \otimes \alpha_3 \otimes \cdots \otimes
      \alpha_k
  \end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        QUANTALE DEFINITION        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}[Quantale $\mathbb{Q}$]
  A quantale is a \emph{lattice} with a binary operator such that for all
    elements of the lattice $x, y$ and $\{x_i\}_i, \{y_i\}_i$
  \begin{align}
    x \oplus \bigvee y_i &= \bigvee x \oplus y_i \\
    \left(\bigvee x_i\right) \oplus y &= \bigvee x_i \oplus y
  \end{align}

  We require that for all $x$, it exist $x^{-1}$ such that
  \begin{align}
    x \oplus x^{-1} &= e \\
    x^{-1} \oplus x &= e
  \end{align}

@@

  On gates
  \begin{align}
    V(f \circ g) &\preceq V(f) \oplus V(g) \\
    V(f \otimes g) &\preceq V(f) \oplus V(g)
  \end{align}

  On rewriting sequences
  \begin{align}
    V(\alpha \circ \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \otimes \beta) &= V(\alpha) \oplus V(\beta) \\
    V(\alpha \bullet \beta) &= V(\alpha) \oplus V(\beta)
  \end{align}
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM REMARK        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
  Note that because
  \[
    V(\alpha: f \Rightarrow g) = V(f) \oplus V(g)^{-1}
  \]
  then
  \begin{align}
    V(\alpha: f \Rightarrow f) &= V(f) \oplus V(f)^{-1} \\
    &= e
  \end{align}
  that is
  \[
    \forall f, V(id_f) = e
  \]
\end{remark}

@@

  \begin{proof}
    The set of all possible rewriting sequences is freely generated by the set
      of rewriting rules, $\bullet$, $\circ$ and $\otimes$ so both $\alpha$ and
      $\beta$ can be written
    \begin{align}
      \alpha &= \alpha_1 \odot \alpha_2 \odot \alpha_3 \odot \cdots \odot
        \alpha_n \\
      \beta &= \beta_1 \odot \beta_2 \odot \beta_3 \odot \cdots \odot \beta_m
    \end{align}
    with $\odot \in \{\bullet, \circ, \otimes\}$ and for all i $\alpha_i$ and
      $\beta_i$ are rewriting rule.
    If $n = 1$ then $\alpha$ is a rewriting rule, so $V(r) = V(f) \oplus
      V(g)^{-1}$.
    Otherwise
    \begin{align}
      V(\alpha) &= V(\alpha_1 \odot \alpha_2 \odot \cdots \odot \alpha_n) \\
      &= V(\alpha_1) \oplus V(\alpha_2) \oplus \cdots \oplus V(\alpha_n) \\
      &= V(f \Rightarrow h_1) \oplus V(h_1 \Rightarrow h_2) \oplus \cdots \oplus
        V(h_n \Rightarrow g) \\
      &= V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus \cdots
        \oplus V(h_n) \oplus V(g)^{-1}
    \end{align}
    A easy inductive proof can show us that
    \[
      V(f) \oplus V(h_1)^{-1} \oplus V(h_1) \oplus V(h_2)^{-1} \oplus V(h_2)
        \oplus \cdots \oplus V(h_n) \oplus V(g)^{-1} = V(f) \oplus V(g)^{-1}
    \]
    The same is true for $\beta$, so
    \[
      V(\alpha) = V(\beta) = V(f) \oplus V(g)^{-1}
    \]
  \end{proof}
\end{proposition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM PROPOSITION 2        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{proposition}
  The following category $\mathcal{P}(\mathbb{Q})$ is a $\mathbb{Q}$-category
  \begin{itemize}
    \item A set of objects which are the gates of $\mathcal{P}$
    \item For all objects $(f, g)$
  \end{itemize}
  \[
    \mathcal{E}(f, g) =
    \begin{cases}
      \textrm{if } f \Rightarrow g \in \mathcal{P}, &V(f \Rightarrow g) \\
      \textrm{otherwise } &\top
    \end{cases}
  \]
  With $\top \in \mathbb{Q}$ such that for all $x \in \mathbb{Q}$
  \[
    x \preceq \top
  \]

  \begin{proof}
    For all gates $(f, g)$, if it exists a unique transformation $f \Rightarrow
      g$, then
    \begin{align}
      \mathcal{E}(f, g) &= V(f \Rightarrow g) \in \mathbb{Q} \\
      &= V(f) \oplus V(g)^{-1}
    \end{align}
    otherwise we already have $\mathcal{E}(f, g) = \top \in \mathbb{Q}$.
    For all gates $f$, we know that there is a identity transformation $f
      \Rightarrow f$ and
    \begin{align}
      \mathcal{E}(f, f) &= V(id_f) \\
      &= V(f \Rightarrow f)\\
      &= V(f) \oplus V(f)^{-1} \\
      &= e
    \end{align}
    Finally, for all gates $(f, g, h)$ such that there exists $\alpha: f
      \Rightarrow g$ and $\beta: g \Rightarrow h$ in $\mathcal{P}$, then the
      homomorphism $V$ give us
    \begin{align}
      \mathcal{E}(f, h) &= V(f \Rightarrow h) \\
      &= V(\alpha \circ \beta) \\
      &= V(\alpha) \oplus V(\beta) \\
      &= V(g \Rightarrow h) \oplus V(f \Rightarrow g) \\
      &= \mathcal{E}(g, h) \oplus \mathcal{E}(f, g)
    \end{align}
    If either $\alpha$ or $\beta$ doesn't exists in $\mathcal{P}$ then
    \[
      \mathcal{E}(b, c) \oplus \mathcal{E}(a, b) \succeq \mathcal{E}(a, c)
    \]
    become
    \[
      \begin{matrix}
        &\mathcal{E}(b, c) \oplus \top &\succeq \top \\
        \textrm{or} &\top \oplus \mathcal{E}(a, b) &\succeq \top \\
        \textrm{or} &\top \oplus \top &\succeq \top
      \end{matrix}
    \]
    which is still true.
  \end{proof}
\end{proposition}

@@

  \begin{proof}
    The monoidal structure is immediate using the fact that
    \[
      V(\alpha) \oplus V(\beta) \succeq V(\alpha \otimes \beta)
    \]
    that is
    \[
      V(\alpha: f \Rightarrow g) \oplus V(\beta: f' \Rightarrow g') = V(\alpha
        \otimes \beta: f \otimes f' \Rightarrow g \otimes g')
    \]
    so
    \[
      \mathcal{E}(f, g) \oplus \mathcal{E}(f', g') = \mathcal{E}(f \otimes f', g
        \otimes g')
    \]
    For the symmetry, we use the fact that $V(f \Rightarrow g) \oplus V(g
      \Rightarrow f) = e$
    \begin{align}
      \mathcal{E}(f \otimes g, g \otimes f) &= V(f \otimes g \Rightarrow g
        \otimes g) \\
      &= V(f \Rightarrow g \otimes g \Rightarrow f) \\
      &\preceq V(f \Rightarrow g) \oplus V(g \Rightarrow f) \\
      &= V(f) \oplus V(g)^{-1} \oplus V(g) \oplus V(f)^{-1} \\
      &= e
    \end{align}
  \end{proof}
\end{proposition}
